MG7: Configurable and scalable 16S data analysis

### 2016-07-25 docs/mg7-paper/out/paper.tex
add ncbi taxonomy to bio4j data
bio4j taxonomy contains ncbi taxonomy

Bio4j \citep{pareja2015bio4j} is a data platform integrating data from
different resources such as UniProt or GO in a graph data paradigm. In
the assignment phase we use a subgraph containing the NCBI Taxonomy,
wrapping in Scala its Java API in a tree algebraic data type.

@@

The hierarchic structure of the taxonomy of the living organisms is a
tree, and, hence, is also a graph in which each node, with the exception
of the root node, has a unique parent node. It led us to model the
taxonomy tree as a graph using the graph database paradigm. Previously
we developed Bio4j \citep{pareja2015bio4j}, a platform for the
integration of semantically rich biological data using typed graph
models. It integrates most publicly available data linked with sequences
into a set of interdependent graphs to be used for bioinformatics
analysis and especially for biological data. MG7 works based on the
Bio4j taxonomy module. It opens the possibility to connect the taxonomic
profiling data obtained with MG7 to all the biological knowledge
associated to each taxon. Using the information available in Bio4j for
all the proteins assigned to each taxon we are connected to all the
functional data available in Uniprot related with it.

>>>>

Bio4j \citep{pareja2015bio4j} is a data platform integrating data from
different resources such as UniProt, the NCBI taxonomy, or GO, in a
graph data paradigm. In the assignment phase we use a subgraph
containing the NCBI Taxonomy, wrapping in Scala its Java API in a tree
algebraic data type.

@@

The hierarchic structure of the taxonomy of the living organisms is a
tree, and, hence, is also a graph in which each node, with the exception
of the root node, has a unique parent node. It led us to model the
taxonomy tree as a graph using the graph database paradigm. Previously
we developed Bio4j \citep{pareja2015bio4j}, a platform for the
integration of semantically rich biological data using typed graph
models. It integrates most publicly available data linked with sequences
into a set of interdependent graphs to be used for bioinformatics
analysis and especially for biological data. MG7 works based on the
Bio4j taxonomy module, which contains all the NCBI taxonomy data. It
opens the possibility to connect the taxonomic profiling data obtained
with MG7 to all the biological knowledge associated to each taxon. Using
the information available in Bio4j for all the proteins assigned to each
taxon we are connected to all the functional data available in Uniprot
related with it.
